Understanding Parameterized Quantum Circuit Learning for Quantum Chemical Applications

### 2025-04-07 manuscript/main.tex
fix hashing tomorrow

Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to explore claims that PQCs offer better model performance using fewer training points and hyperparameters.\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020}
For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig. \ref{fig:BSE5_learning_curves}.
Across the learning curve, the \textit{k}-NN model has a mean R$^{2}$s of 0.9998 for the training set and 0.5822 test set, while M-M-CZ{\_}HWE-CNOT has a mean R$^{2}$ of 0.1405 for the training set and R$^{2}$ of 0.136 for the test set.
For M-M-CZ{\_}HWE-CNOT, the training set performance peaks when using 10\% of the training data with an R$^{2}$ of 0.2015, dips to an R$^{2}$ of -0.0172 using 30\% of the training data, and then maintains an R$^{2}$ less than 0.2 for the remaining percentages of the training data.
Unlike the training points, the test reaches peak performance when 70\% of the total data is used in the training set, with a test R$^{2}$ of 0.2064.

>>>>

Following the analysis of the RUD and number of ALs for both 5 qubit models, we explored claims that PQCs offer better model performance using fewer training points and hyperparameters\cite{schuld_circuit-centric_2020,du_expressive_2020,suzuki_predicting_2020} using learning curves.
Our learning curves are generated varying the number of training points from 10-80\% of the total data, while fixing the number of test points to 20\% of the total dataset.
In Fig. \ref{fig:learningcurves}, we analyze the effects of the number of training points of the best 5 qubit BSE49 and DDCC circuits, M-M-CZ{\_}HWE-CNOT using a RUD and AL of 1 and A2{\_}HWE-CNOT using a RUD of 
Next, we use learning curves, where the number of training points is varied, while the number of training points is varied to 
For the BSE49 dataset, using 5 qubits, we found that M-M-CZ{\_}HWE-CNOT offers less overfit models, but offer poorer performance regarding the training and test set R$^{2}$s, as highlighted in Fig. \ref{fig:BSE5_learning_curves}.
Across the learning curve, the \textit{k}-NN model has a mean R$^{2}$s of 0.9998 for the training set and 0.5822 test set, while M-M-CZ{\_}HWE-CNOT has a mean R$^{2}$ of 0.1405 for the training set and R$^{2}$ of 0.136 for the test set.
For M-M-CZ{\_}HWE-CNOT, the training set performance peaks when using 10\% of the training data with an R$^{2}$ of 0.2015, dips to an R$^{2}$ of -0.0172 using 30\% of the training data, and then maintains an R$^{2}$ less than 0.2 for the remaining percentages of the training data.
Unlike the training points, the test reaches peak performance when 70\% of the total data is used in the training set, with a test R$^{2}$ of 0.2064.
